Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-03-18 ms.tex
I started an observations summary table.
I edited the introduction and some references.

\section{Introduction}

@@

\section{Acknowledgements}
Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the Kuiper 61-inch telescope.
MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research made use of the \texttt{astropy} package \citep{astropy2013}.

>>>>

\section{Introduction}
The disintegrating planet candidate KIC 12557548 b \citep{rappaport} was the first discovery of a planet candidate causes wildly varying dust obscuration of its host star.
It is now one of many systems that are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.

The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
During this time, the transit depths averaged around (??0.55\%) but varied stochastically from just one 15.7 hour orbit to the next.
\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations all fell during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.

\begin{deluxetable*}{lr}
\tablecaption{List of observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date} & Comment \\
UT & \\
 }
\startdata
UT 2016-06-10 & Clouds \\
UT 2016-06-12 & Good \\
UT 2016-06-14 & Good \\
UT 2016-07-12 & Good \\
UT 2016-07-14 & Good \\
UT 2016-07-16 & Good \\
\enddata
\tablenotetext{}{Obs Summary.}
\end{deluxetable*}

@@

\section{Acknowledgements}
Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research made use of the \texttt{astropy} package \citep{astropy2013}.
